CO($J$ = 3 $\rightarrow$ 2) observation in a strongly lensed type-2 quasar host SMG at $z$ = 2.221 with continuum detection in the foreground lensing FR-II radio galaxy at $z$ = 0.685

### 2015-06-23 skeleton.tex
hard wrap lines, fixed CARMA obs section

\begin{abstract}
We report the detection of CO($J$ = 3 $\rightarrow$ 2) line emission in SMM J0939+8315 ($z$ = 2.221), a
strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
foreground FR-II radio galaxy and a companion galaxy at $z$ = 0.685. We perform lens modeling on the Submillimeter Array (SMA) 1 mm dust continuum, resulting a
lensing magnification factor of $\mu=$9.7 $\pm$ 1.4. This allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background quasar host SMG. Prior to correcting for lensing amplification, we measure the
velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s$^{-1}$,
corresponding to a lensing-corrected CO($J$ = 1 $\rightarrow$ 0) line luminosity of $L^{\prime}_{\rm CO(1-0)}$ = (4.1 $\pm$ 0.9) $\times$ 10$^{10}$ K km s$^{-1}$ pc$^2$. This
translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$, assuming a conversion
factor of $\alpha_{\rm CO}$=0.8 $M_{\odot}$ (K km s$^{-1}$ pc$^2$)$^{-1}$. We report marginally resolved continuum emission from the foreground radio galaxy 3C220.3 with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
 at 104 GHz (1.7 mm rest-frame), allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We fit
 both an optically thick and optically thin modified blackbody models to the SED of the SMG using existing
infrared photometric data. Our SED fitting favours an optically thick model, yielding dust mass of $M_{\rm
dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8 M_{\odot}$, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}_{-2.6}\times$10$^{12}L_{\odot}$, prior to lensing correction. We conclude that the properties (e.g., gas mass, gas mass fraction, SFR) of the molecular gas reservoir in SMM
J0939+8315 based on our CO($J$ = 3 $\rightarrow$ 2) observation is similar to other high redshift
SMGs. \\
NEED TO  FIX: 
report SFR, gas-to-dust ratio..
The dust blah, and other properties similar to existing blah (M gas is similar to HLSW-01), This study blah?. the
population.\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
% Junk intro
%Submillimeter galaxies (SMGs) are typically dust-enshrouded star-forming
%galaxies at z $>$ 1, and their dust component in the interstellar medium (ISM)
%gives rise to the observed-frame submm peak of the spectral energy
%distribution (SED), providing a way to detect them with (sub)mm facilities.
%Most of the brightest SMGs discovered to date are strongly lensed, magnifying
%the intrinsic fluxes of these distant galaxies (Negrello et al. 2010, Wardlow
%et al. 2013). Gravitational lensing enables us to detect and resolve the dusty
%star-forming galaxies at higher physical resolution than otherwise possible. \\
%Much studies in the past 17 years focus in understanding the role of submillimeter/FIR selected galaxies at the
%peak epoch of cosmic star formation.  at $z \sim$ 2-3 to study galaxy formation and evolution. Great progress
%has been made over the past 15 years in understanding the role of submillimeter-selected galaxies (SMGs), and
%AGN evolution in the study of galaxy evolution.

This paragraph: The population at high z: \newline
%Dusty luminous high-z galaxies have been unveiled through their high submm flux densities. bright, submm continuum-
%selected galaxies (SMGs) with S850\micron $>$ 5mJy are dusty and gas-rich, very luminous ($\sim$ 10$^{13}$ L
%$_\odot$) galaxies with SFR $\sim$ 10$^3$ M$_\odot$ yr$^{-1}$ (blain et al. 2002, Chapman et al. 2005, Smail
%et al. 2002).
%
%detect Molecular emission, line profiles in the CO($J$ = 3 $\rightarrow$ 2) rotational lines. SMG are systems with
%a
%significant fraction of the available initial gas reservoir of 10$^{10}$ - 10$^{11}$ M$_\odot$. Converted to stars
%over several dynamical timescales, typically $\sim$ 10$^8$ yr. Physical properties of high-z star-forming galaxies.

@@

We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km Mpc$^{-1}$
s$^{-1}$, $\Omega_{\rm M}$ = 0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results (Hinshaw et al. 2013).
The luminosity distances at $z$ = 0.685 and $z$ = 2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
corresponds to 8.406 kpc at $z$ = 2.221, and 7.169 kpc at $z$ = 0.685.

%\section{Data and Observations}\label{sec:obs}
\section{Observations}\label{sec:obs}
%\subsection{Previous Data} \label{sec:previousdata}
%%The SMG fits the paradigm of a composite AGN/starburst galaxy in the early Universe.
%%Both the rest-frame UV (218 nm) image obtained using the Hubble Space Telescope (HST) and the spectral line
%%measurements of C IV 1549 and He II
%%1640 from Keck LRIS show that the SMG is likely to be hosting a type-2 quasar \citep{Haas14}. Furthermore,
%%the offset of the UV emission suggests
%%that this galaxy is undergoing the breakup of its dust cocoon, an important transition phase in starburst galaxies
%
%Due to the peculiarity of this lens system, the system has been followed up extensively with ultraviolet (UV),
%optical, IR, sub-mm, and radio observations for the last decade using the Hubble Space Telescope (HST), the Keck Observatory, the {\it Herschel} Space Telescope, the Spitzer Space Telescopes, the Submillimeter Array (SMA), respectively \citep{Haas14}. The redshifts of the galaxies in this systems are spectroscopically confirmed.
%Combining the infrared photometric data with our CARMA measurement, we study the properties of these dust and molecular gas of the ISM in the SMG. We perform lens modeling using existing archival SMA 1 mm data (P.I. S. Willner), observed on 2013 February 10. Details of the SMA observation is described by \citet{Haas14}.

\subsection{CARMA} \label{sec:carmadata}
% this section ok
%CO($J$ = 3 $\rightarrow$ 2)
% total obs time = 3.2 hours,
% Total on source time = 1.56 hours
% 16 windows, each 0.494792 GHz with 95 channels
% rms per channel. (29.xx km/s) xx mjy per beam

Observation of the CO($J$ = 3 $\rightarrow$ 2) rotation line ($\nu_{rest}$ = 345.7959899 GHz),
redshifted to $\nu_{obs}$ = 107.3567183 GHz (2.794 mm) towards the background galaxy SMM
J0939+8315 ($z$ = 2.221) was carried out using the CARMA (P.I. D. Riechers).
We used the 3mm receiver with a bandwidth of 3.75 GHz on each sideband, at 5.208 MHz (14.544 km s$^{-1}$)
resolution to cover the CO($J$ = 3 $\rightarrow$ 2) line and the underlying 2.877 mm (1.707 mm at $z$ = 0.685)
continuum emission. The CO($J$ = 3 $\rightarrow$ 2) line was placed on the
upper sideband with the local oscillator frequency tuned to $\nu_{\rm LO}$ = 104.2609 GHz.
Observation was carried out under good
weather conditions at in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator and the nearby quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The MIRIAD package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with "natural" weighting, this yields a synthesized (clean) beam size of 13$\farcs$57 $
\pm$ 1\farcs4 $\times$ 5\farcs77 $\pm$ 3\farcs1. The final rms noise is $\sigma$ = 12 mJy $\rm beam^{-1}$ over
a channel width of 10.416 MHz (corresponding to 29.088 km s$^{-1}$). The continuum image is created by
averaging over all the line-free channels, this yields a synthesized (clean) beam size of 16\farcs67 $\pm
$ 0\farcs69 $\times$ 7\farcs17 $\pm$ 1\farcs60 and a rms noise of 0.547 mJy beam$^{-1}$.

\section{Results}\label{sec:res}
\subsection{New results: Continuum Emission} %%% ok
%%Continuum: 104.2106 GHz (2.876794 mm observed frame)
% So integrated - peak should be approx. the extended components ~ (7.18 +/- 0.69 mJy - 5.56 +/- 0.54 mJy)
% max peak = 0.005347 \pm 5.0e-4
% VLA sigma = 6.41094e-05 Jy

%Deconvolution size bigger than expected (= just radio core):
%1) phase error that wasn't well calibrated (~30/360 $\times$\appox 16") ~ 1-2"
%2) low SNR giving rise to fitting error ~ 4" from `imfit`
%3) PA beam align with RG (radio galaxy) orientation
Averaging over all the line-free channels, we detect the radio continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 mJy at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame. In this lens system, the foreground galaxy (3C220.3) is radio-loud, hence we expect the continuum to be dominated by the foreground galaxy. The deconvolved source size of the continuum image is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60. At this frequency, we expect the emission from the radio core to dominate our continuum detection; however, the integrated flux density is measured to be 7.18 $\pm$ 0.69 mJy. Considering the fact that the orientation of the synthesized beam aligns with the axis along the lobes of the foreground radio galaxy as shown in Figure \ref{fig:cont}, we interpret this difference between the peak flux density and the integrated flux density as the source (core and lobes) being partially resolved, i.e., the continuum detection includes non-thermal emission from the lobes.
\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel}
\caption{The central cross indicates the position of the radio core of 3C220.3. Contour levels of the 9 GHz continuum emission start at $\pm$4$\sigma$ of $\sigma$ = 0.0641 mJy beam$^{-1}$ and increment at steps of $\pm$2$^n\sigma$, where n is positive integers; contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps of $\pm$1$\sigma$ of 0.5 mJy beam$^{-1}$.
Left:Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 16\farcs67 $\times$ 7\farcs17, at P.A. = -58$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the foreground radio galaxy 3C220.3 overlaid the 9 GHz emission (green) \citep{Haas14}. The rms in the 9GHz image is $\sigma$ = 0.0641 mJy beam$^{-1}$. The synthesized beam size of the VLA observations is 0$\farcs$60 $\times$ 0$\farcs$23 at P.A. 76$\degr$. 
\label{fig:cont}}
\end{figure*}

\subsection{New results: CO($J$ = 3 $\rightarrow$ 2) line emission}
%peak 19.907623291015625 2.2045940408007811
%We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward SMM J0939+8315 at peak flux
%of blah sigma  of $ \sigma$ = blah mJy beam$^{-1}$.
We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background SMG SMM J0939+8315. We extract the spectrum and fit a single-component Gaussian as shown in Figure \ref{fig:mom0}, yielding peak flux density of 19.90 $\pm$ 2.20 mJy, superimposed on a continuum level of 3.46 mJy, the FWHM of the Gaussian fit is 541.65 $\pm$ 31.91 km s$^{-1}$. The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, where the synthesized beam size of the SMA observation is 1\farcs42$\times$1\farcs16, at P.A. -34.0\degr. Since the angular resolution of our CO measurement is 13$\farcs$57 $\times$ 5\farcs77 , the CO($J$ = 3 $\rightarrow$ 2) detection in the SMG is therefore spatially unresolved. We construct the velocity-integrated (moment-0) map of the CO($J$ = 3 $\rightarrow$ 2) emission using the uv-continuum subtracted data, the velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line flux is 14.6 $\pm$ 0.9 Jy km s$^{-1}$.

@@

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel}
\includegraphics[width=0.65\textwidth]{Figure/peak28_WiderSpectrum}
\caption{The central cross represents the coordinates for alignment between plots. The contour starts at $\pm$3$\sigma$, incrementing at
steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the CO($J$ = 3 $\rightarrow$ 2) line emission in the background SMG with $\sigma$ = 0.7 Jy km s$^{-1}$ beam$^{-1}$. The angular resolution is 13$\farcs$57 $\times$ 5\farcs77, the beam size is shown in the bottom left corner. 
Top Right: Contours of CO($J$ = 3 $\rightarrow$ 2) emission (red) overlaid on the SMA 1 mm dust continuum (green) with $\sigma$ = 0.84 mJy beam$^{-1}$. The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A. -34\degr, as shown in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam size of the CARMA observations, hence the CO($J$ = 3 $\rightarrow$ 2) line detection is spatially unresolved.
%Bottom: The Gaussian-fitted line peak of CO($J$ = 3 $\rightarrow$ 2) is 23.36 $\pm$ 2.21 mJy (before continuum
%subtraction), and the integrated line flux over linewidth of $\sim$1000 km/s is 14.6 $\pm$ 0.9 Jy km s$^{-1}$
%(after continuum subtraction).  
Bottom: Solid black line shows our Gaussian fit to the CO ($J$ = 3 $\rightarrow$ 2) line profile. Yellow histogram shows the flux density as a function of velocity offset, where 0 km/s corresponds to $z$ = 2.2214. 
\label{fig:mom0}}
\end{figure*}

@@

\begin{figure}[!tbp]
\centering
\includegraphics[width=0.5\textwidth]{Figure/CorrelationPlot__thick_testbeta}
\includegraphics[width=0.5\textwidth]{Figure/CorrelationPlot__thin_testSMA}
\caption{Resulting correlation plot from our SED fitting. Plots on the diagonal axes are marginalized posterior probability distribution of each
parameter. Off-diagonal plots are 2D histograms between parameters. Cross denotes where the best-fit value corresponds to in the 2D correlation plot. Top: Optically thick
model. Bottom: Optically thin model. The parameter T is the observed-frame characteristic dust temperature.\label{fig:sedlikelihood}}
\end{figure}
%Our uncertainties on M$_{d}$ do not include the uncertainty in $K_{\nu}$, which is at least a factor of blah dex.
%In most cases, $\alpha$ is poorly constrained, with the fits only providing a lower limit. Because of the way the
%blue-side power law is joined to the MBB,
%this simply amounts to a statement that the merge point between the power law and the thermal SED lies at
%wavelengths lower than the shortest
%wavelength photometry point (250 micron). (in Dowell et al. 2014)
% Compare to Haas SED
%The SED based on the dust emission of the background SMG in 250-1000 $\micron$ is best fitted with dust
%temperature T$_{\rm d}$ $\sim$ 36 K at z = 2.221 fixing dust emissivity index $\beta$ = 1.5,
%their the intrinsic FIR luminosity from the background source is L$_{\rm FIR}$ = 1 $\times$ 10$^{13}$ L$_{\odot}$

@@

Since only CO($J$ = 3 $\rightarrow$ 2) line has been detected on this object, we derive the molecular gas mass in
this SMG assuming thermalized excitation or assuming thermalized optically thick CO, i.e. the brightness temperature ratio between CO($J$ = 3 $\rightarrow$ 2)
and ($J$ = 1 $\rightarrow$ 0) is $R_{31}$ = 1 (e.g., Riechers et al. 2011; Ivison et al. 2008, 2012; Scott et
al. 2011). We calculate the CO($J$ = 1 $\rightarrow$ 0) line luminosity using standard relations (e.g., Solomon \&
van den Bout 2005; Carilli \& Walter 2013):
\begin{equation}
L^{\prime}_{\rm CO} = \frac{3.25\times10^7}{\nu_{\rm CO (3-2), rest}^2}\times \frac{D_L^2}{\mu} \times
\frac{I_{\rm CO(3-2)}} {R_{\rm 31} (1 + z)}
\end{equation}
this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ ($\mu$/9.74)$^{-1}$ [\rm K km s$^{-1}$ pc$^2$]
after lensing correction. The inferred total molecular gas mass is therefore M$_{\rm gas}$ = 3.303$\times
$10$^{10}$ ($\alpha$/0.8) ($\mu$/9.74)$^{-1} M_\odot$. We assume a conversion factor of $\alpha_{\rm CO}$ =
0.8 M$_\odot$ (K Km s$^{-1}$ pc$^2$)$^{-1}$ based on empirical relations from local ULIRGs, which is typically
adopted for SMGs \citep{Bothwell13a,Tacconi10a,Daddi2010a}. As derived in the previous section, SMM has a dust mass of M$_{\rm dust}
$=50.47$^{20.42}_{-20.15}\times$10$^8\rm M_{\odot}$ (before lensing correction), this corresponds to a gas-to-dust
ratio of f$_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 63.74 $\pm$ blah , which is in good agreement with the range of values found in other SMGs (cite).

>>>>

\begin{abstract}
We report the detection of CO($J$ = 3 $\rightarrow$ 2) line emission in SMM J0939+8315 ($z$ = 2.221), a
strongly lensed high-redshift submillimeter galaxy (SMG) hosting a type-2 quasar using
the Combined Array for Research in Millimeter-wave Astronomy (CARMA). This lensing system consists of a
foreground FR-II radio galaxy and a companion galaxy at $z$ = 0.685. We perform lens modeling on the Submillimeter Array 
(SMA) 1 mm dust continuum, resulting a
lensing magnification factor of $\mu=$9.7 $\pm$ 1.4. This allows us to place constraints on the intrinsic properties
of the cold gas and dust in the interstellar medium (ISM) of the background quasar host SMG. Prior to correcting for lensing 
amplification, we measure the
velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line intensity of $I_{\rm CO(3-2)}$ = (14.6 $\pm$ 0.9) Jy km s$^{-1}$,
corresponding to a lensing-corrected CO($J$ = 1 $\rightarrow$ 0) line luminosity of $L^{\prime}_{\rm CO(1-0)}$ = (4.1 $\pm$ 
0.9) $\times$ 10$^{10}$ K km s$^{-1}$ pc$^2$. This
translates to a molecular gas mass of $M_{\rm gas}$ = 3.3 $\times$ 10$^{10}M_\odot$, assuming a conversion
factor of $\alpha_{\rm CO}$=0.8 $M_{\odot}$ (K km s$^{-1}$ pc$^2$)$^{-1}$. We report marginally resolved continuum 
emission from the foreground radio galaxy 3C220.3 with peak flux density of $S_\nu$ = 5.56 $\pm$ 0.54 mJy
 at 104 GHz (1.7 mm rest-frame), allowing us to put constraints on the spectral energy distribution (SED) of this galaxy. We 
fit
 both an optically thick and optically thin modified blackbody models to the SED of the SMG using existing
infrared photometric data. Our SED fitting favours an optically thick model, yielding dust mass of $M_{\rm
dust}$ = 50.5$^{20.4}_{-20.2}$ $\times$ 10$^8 M_{\odot}$, and total infrared (IR) luminosity of $L$ = 88.5$^{+2.6}
_{-2.6}\times$10$^{12}L_{\odot}$, prior to lensing correction. We conclude that the properties (e.g., gas mass, gas mass 
fraction, SFR) of the molecular gas reservoir in SMM
J0939+8315 based on our CO($J$ = 3 $\rightarrow$ 2) observation is similar to other high redshift
SMGs. \\
NEED TO  FIX: 
report SFR, gas-to-dust ratio..
The dust blah, and other properties similar to existing blah (M gas is similar to HLSW-01), This study blah?. the
population.\end{abstract}
\keywords{galaxies: formation --- galaxies: high-redshift --- submillimeter: galaxies}

\section{Introduction}\label{sec:intro}
This paragraph: The population at high z: \newline
%Dusty luminous high-z galaxies have been unveiled through their high submm flux densities. bright, submm continuum-
%selected galaxies (SMGs) with S850\micron $>$ 5mJy are dusty and gas-rich, very luminous ($\sim$ 10$^{13}$ L
%$_\odot$) galaxies with SFR $\sim$ 10$^3$ M$_\odot$ yr$^{-1}$ (blain et al. 2002, Chapman et al. 2005, Smail
%et al. 2002).
%
%detect Molecular emission, line profiles in the CO($J$ = 3 $\rightarrow$ 2) rotational lines. SMG are systems with
%a
%significant fraction of the available initial gas reservoir of 10$^{10}$ - 10$^{11}$ M$_\odot$. Converted to stars
%over several dynamical timescales, typically $\sim$ 10$^8$ yr. Physical properties of high-z star-forming galaxies.

@@

We adopt a standard $\Lambda$CDM cosmological model throughout this paper, with H$_0$= 69.32 km Mpc$^{-1}$
s$^{-1}$, $\Omega_{\rm M}$ = 0.286, $\Omega_\Lambda$=0.713, based on WMAP9 results \citep{Hinshaw13a}.
The luminosity distances at $z$ = 0.685 and $z$ = 2.221 are 4214 Mpc and 19052 Mpc, respectively; 1$\arcsec$
corresponds to 8.406 kpc at $z$ = 2.221, and 7.169 kpc at $z$ = 0.685.

\section{Observations}\label{sec:obs}
\subsection{CARMA} \label{sec:carmadata}
%CO($J$ = 3 $\rightarrow$ 2)
% total obs time = 3.2 hours,
% Total on source time = 1.56 hours
% 16 windows, each 0.494792 GHz with 95 channels
% rms per channel. (29.xx km/s) xx mjy per beam

Observations of the CO($J$ = 3 $\rightarrow$ 2) rotation line ($\nu_{rest}$ = 345.7959899 GHz),
redshifted to $\nu_{obs}$ = 107.357 GHz (2.794 mm) towards the background galaxy SMM
J0939+8315 ($z$ = 2.221) were carried out using CARMA (programme ID: cf0142; P.I.: D. Riechers).
We used the 3mm receivers with a bandwidth of 3.75 GHz in each sideband, at 5.208 MHz ($\sim$14.5 km s$^{-1}$)
resolution to cover the CO($J$ = 3 $\rightarrow$ 2) line and the underlying 2.877 mm continuum emission. The CO($J$ = 3 
$\rightarrow$ 2) line was placed on the
upper sideband with the local oscillator frequency tuned to $\nu_{\rm LO}$ = 104.2609 GHz.
Observations were carried out under good
weather conditions in the E array configuration on 2014 July 12. This resulted in 1.56 hours of 15 antenna-
equivalent on-source time after discarding unusable visibility data.
The nearby source J1039+811 (0.65Jy) was observed every 20 minutes for
pointing, amplitude, and phase calibration. Mars was observed as the primary
absolute flux calibrator and the quasar 3C273 was observed as the secondary
flux calibrator. J0927+390 was observed for bandpass calibration, yielding $\sim
$15\% calibration accuracy.
The MIRIAD package was used to calibrate and analyze the visibility data, which are deconvolved and imaged using
the CLEAN algorithm with ``natural" weighting, this yields a synthesized (clean) beam size of 13$\farcs$57 $\times$ 
5\farcs77 . The final rms noise is $\sigma$ = 0.7 Jy $\rm beam^{-1}$ over
a channel width of 135.4 MHz (corresponding to $\sim$378.1 km s$^{-1}$). The continuum image is created by
averaging over all the line-free channels, this yields a synthesized (clean) beam size of 16\farcs67 $\times$ 7\farcs17 and a 
rms noise of 0.55 mJy beam$^{-1}$.

% mom0 map channels [72, 85], each channel is 29.088 km/s, i.e. total velocity range is 378.144 km/s, which is 135.408 
MHz
\section{Results}\label{sec:res}
\subsection{New results: Continuum Emission}

%%Continuum: 104.2106 GHz (2.876794 mm observed frame)
% So integrated - peak should be approx. the extended components ~ (7.18 +/- 0.69 mJy - 5.56 +/- 0.54 mJy)
% max peak = 0.005347 \pm 5.0e-4
% VLA sigma = 6.41094e-05 Jy

%Deconvolution size bigger than expected (= just radio core):
%1) phase error that wasn't well calibrated (~30/360 $\times$\appox 16") ~ 1-2"
%2) low SNR giving rise to fitting error ~ 4" from `imfit`
%3) PA beam align with RG (radio galaxy) orientation
Averaging over all the line-free channels, we detect the continuum with peak flux density of S$_\nu$ = 5.56 $\pm$ 0.54 
mJy at an averaged frequency of $\nu_{cont}$ = 104.2106 GHz (2.877 mm) in the observed-frame. In this lens system, the 
foreground galaxy (3C220.3) is radio-loud, hence we expect the continuum to be dominated by the foreground galaxy. The 
deconvolved source size of the continuum image is 8\farcs72 $\pm$ 0\farcs69 $\times$ 3\farcs87 $\pm$ 1\farcs60. At this 
frequency, we expect the emission from the radio core to dominate our continuum detection; however, the integrated flux 
density is measured to be 7.18 $\pm$ 0.69 mJy. Considering the fact that the orientation of the synthesized beam aligns with 
the axis along the lobes of the foreground radio galaxy as shown in Figure \ref{fig:cont}, we interpret this difference between 
the peak flux density and the integrated flux density as the source (core and lobes) being partially resolved, i.e., the 
continuum detection includes non-thermal emission from the lobes.
\begin{figure*}[tbph]
\centering
\includegraphics[width=0.80\textwidth]{Figure/ContPanel}
\caption{The central cross indicates the position of the radio core of 3C220.3. Contour levels of the 9 GHz continuum 
emission start at $\pm$4$\sigma$ of $\sigma$ = 0.0641 mJy beam$^{-1}$ and increment at steps of $\pm$2$^n\sigma$, 
where n is positive integers; contour levels of the 104 GHz continuum emission start at $\pm$3$\sigma$, incrementing at steps 
of $\pm$1$\sigma$ of 0.5 mJy beam$^{-1}$.
Left:Contour map of the 104 GHz continuum emission in 3C220.3. The beam size is 16\farcs67 $\times$ 7\farcs17, at P.A. = 
-58$\degr$, as indicated in the bottom left corner. Right: Contours of the CARMA 104 GHz continuum emission (red) from the 
foreground radio galaxy 3C220.3 overlaid the 9 GHz emission (green) \citep{Haas14}. The rms in the 9GHz image is $\sigma$ 
= 0.0641 mJy beam$^{-1}$. The synthesized beam size of the VLA observations is 0$\farcs$60 $\times$ 0$\farcs$23 at P.A. 
76$\degr$. 
\label{fig:cont}}
\end{figure*}

\subsection{New results: CO($J$ = 3 $\rightarrow$ 2) line emission}
%peak 19.907623291015625 2.2045940408007811
%We have detected unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward SMM J0939+8315 at peak flux
%of blah sigma  of $ \sigma$ = blah mJy beam$^{-1}$.
We detect unresolved CO($J$ = 3 $\rightarrow$ 2) line emission toward the background SMG SMM J0939+8315. We extract 
the spectrum and fit a single-component Gaussian as shown in Figure \ref{fig:mom0}, yielding peak flux density of 19.90 $\pm
$ 2.20 mJy, superimposed on a continuum level of 3.46 mJy, the FWHM of the Gaussian fit is 541.65 $\pm$ 31.91 km s
$^{-1}$. The spatial extent of the SMG is shown in the SMA 1 mm dust continuum in Figure \ref{fig:mom0}, where the 
synthesized beam size of the SMA observation is 1\farcs42$\times$1\farcs16, at P.A. -34.0\degr. Since the angular resolution 
of our CO measurement is 13$\farcs$57 $\times$ 5\farcs77 , the CO($J$ = 3 $\rightarrow$ 2) detection in the SMG is 
therefore spatially unresolved. We construct the velocity-integrated (moment-0) map of the CO($J$ = 3 $\rightarrow$ 2) 
emission using the uv-continuum subtracted data, the velocity-integrated CO($J$ = 3 $\rightarrow$ 2) line flux is 14.6 $\pm$ 
0.9 Jy km s$^{-1}$.

@@

\begin{figure*}[tbph] 
\centering
\includegraphics[width=0.8\textwidth]{Figure/LinePanel}
\includegraphics[width=0.65\textwidth]{Figure/peak28_WiderSpectrum}
\caption{The central cross represents the coordinates for alignment between plots. The contour starts at $\pm$3$\sigma$, 
incrementing at
steps of $\pm$1$\sigma$. Top Left: Continuum-subtracted moment-0 map of the CO($J$ = 3 $\rightarrow$ 2) line emission in 
the background SMG with $\sigma$ = 0.7 Jy km s$^{-1}$ beam$^{-1}$. The angular resolution is 13$\farcs$57 $\times$ 
5\farcs77, the beam size is shown in the bottom left corner. 
Top Right: Contours of CO($J$ = 3 $\rightarrow$ 2) emission (red) overlaid on the SMA 1 mm dust continuum (green) with $
\sigma$ = 0.84 mJy beam$^{-1}$. The beam size of the SMA data is 1\farcs42$ \times $1\farcs16, P.A. -34\degr, as shown 
in the bottom left corner. From this image, it is apparent that the extent of the background SMG is smaller than the beam 
size of the CARMA observations, hence the CO($J$ = 3 $\rightarrow$ 2) line detection is spatially unresolved.
%Bottom: The Gaussian-fitted line peak of CO($J$ = 3 $\rightarrow$ 2) is 23.36 $\pm$ 2.21 mJy (before continuum
%subtraction), and the integrated line flux over linewidth of $\sim$1000 km/s is 14.6 $\pm$ 0.9 Jy km s$^{-1}$
%(after continuum subtraction).  
Bottom: Solid black line shows our Gaussian fit to the CO ($J$ = 3 $\rightarrow$ 2) line profile. Yellow histogram shows the 
flux density as a function of velocity offset, where 0 km/s corresponds to $z$ = 2.2214. 
\label{fig:mom0}}
\end{figure*}

@@

\begin{figure}[!tbp]
\centering
\includegraphics[width=0.5\textwidth]{Figure/CorrelationPlot__thick_testbeta}
\includegraphics[width=0.5\textwidth]{Figure/CorrelationPlot__thin_testSMA}
\caption{Resulting correlation plot from our SED fitting. Plots on the diagonal axes are marginalized posterior probability 
distribution of each
parameter. Off-diagonal plots are 2D histograms between parameters. Cross denotes where the best-fit value corresponds to in 
the 2D correlation plot. Top: Optically thick
model. Bottom: Optically thin model. The parameter T is the observed-frame characteristic dust temperature.
\label{fig:sedlikelihood}}
\end{figure}
%Our uncertainties on M$_{d}$ do not include the uncertainty in $K_{\nu}$, which is at least a factor of blah dex.
%In most cases, $\alpha$ is poorly constrained, with the fits only providing a lower limit. Because of the way the
%blue-side power law is joined to the MBB,
%this simply amounts to a statement that the merge point between the power law and the thermal SED lies at
%wavelengths lower than the shortest
%wavelength photometry point (250 micron). (in Dowell et al. 2014)
% Compare to Haas SED
%The SED based on the dust emission of the background SMG in 250-1000 $\micron$ is best fitted with dust
%temperature T$_{\rm d}$ $\sim$ 36 K at z = 2.221 fixing dust emissivity index $\beta$ = 1.5,
%their the intrinsic FIR luminosity from the background source is L$_{\rm FIR}$ = 1 $\times$ 10$^{13}$ L$_{\odot}$

@@

Since only CO($J$ = 3 $\rightarrow$ 2) line has been detected on this object, we derive the molecular gas mass in
this SMG assuming thermalized excitation or assuming thermalized optically thick CO, i.e. the brightness temperature ratio 
between CO($J$ = 3 $\rightarrow$ 2)
and ($J$ = 1 $\rightarrow$ 0) is $R_{31}$ = 1 (e.g., Riechers et al. 2011; Ivison et al. 2008, 2012; Scott et
al. 2011). We calculate the CO($J$ = 1 $\rightarrow$ 0) line luminosity using standard relations (e.g., Solomon \&
van den Bout 2005; Carilli \& Walter 2013):
\begin{equation}
L^{\prime}_{\rm CO} = \frac{3.25\times10^7}{\nu_{\rm CO (3-2), rest}^2}\times \frac{D_L^2}{\mu} \times
\frac{I_{\rm CO(3-2)}} {R_{\rm 31} (1 + z)}
\end{equation}
this corresponds to $L^{\prime}_{\rm CO (1-0)}$ = (4.13 $\pm$ 0.87) $\times$ 10$^{10}$ ($\mu$/9.74)$^{-1}$ [\rm K km s
$^{-1}$ pc$^2$]
after lensing correction. The inferred total molecular gas mass is therefore M$_{\rm gas}$ = 3.303$\times
$10$^{10}$ ($\alpha$/0.8) ($\mu$/9.74)$^{-1} M_\odot$. We assume a conversion factor of $\alpha_{\rm CO}$ =
0.8 M$_\odot$ (K Km s$^{-1}$ pc$^2$)$^{-1}$ based on empirical relations from local ULIRGs, which is typically
adopted for SMGs \citep{Bothwell13a,Tacconi10a,Daddi2010a}. As derived in the previous section, SMM has a dust mass of M
$_{\rm dust}
$=50.47$^{20.42}_{-20.15}\times$10$^8\rm M_{\odot}$ (before lensing correction), this corresponds to a gas-to-dust
ratio of f$_{\rm gas-dust}$ = $M_{\rm gas}/M_{\rm dust}$ = 63.74 $\pm$ blah , which is in good agreement with the range 
of values found in other SMGs (cite).
